Development of Performance Regression Analysis Tool using Distributed Tracing on Microservice-based Application\\

### 2022-06-23 paper.tex
txs auto checkin

\subsection{Overhead Testing}
Of the 11 test cases, the average PRA Engine tool uses 0.046
vCPU with standard deviation of 0.0038 and 154.41 MiB Memory with standard
deviation of 17.91 in one analysis. The entire cluster has resources
as much as 6 vCPUs and 22.5 GiB, so that in one time doing PRA Engine analysis
resulting in CPU overhead as much as 0.78\% and Memory as much as 0.67\% to the Kubernetes cluster. Overhead caused by the tool is low so that the use of PRA Engine tools will have no impact on the overall performance of the Kubernetes cluster. Table \ref{overhead-tbl} shows the result of the overhead testing.
\begin{table}[!htb]
	\caption{Overhead testing result}
	\label{overhead-tbl}
	\centering
	\begin{tabular}{|l|c|c|}
		\hline
		ID & CPU (vCPU) & Memory (MiB) \\
		\textbf{IS1}     & 0,042 & 137,82  \\ \hline
		\textbf{IS2}     & 0,043 & 128,71  \\ \hline
		\textbf{IS3}     & 0,04  & 131,55  \\ \hline
		\textbf{IS4}     & 0,045 & 146,6   \\ \hline
		\textbf{IS5}     & 0,046 & 153,61  \\ \hline
		\textbf{IS6}     & 0,047 & 152,71  \\ \hline
		\textbf{Is7}     & 0,048 & 152,71  \\ \hline
		\textbf{ES1}     & 0,049 & 168,8   \\ \hline
		\textbf{ES2}     & 0,05  & 183,68  \\ \hline
		\textbf{ES3}     & 0,051 & 176,59  \\ \hline
		\textbf{ES4}     & 0,052 & 165,75  \\ \hline
		\textbf{Average} & 0,046 & 154,411 \\ \hline
		\textbf{STD}     & 0,038 & 17,916  \\ \hline
	\end{tabular}
\end{table}
\pagebreak

@@

Fig. \ref{result_log_1} shows the log obtained from the IS1 case with a significant value 0.05. It can be seen that the \texttt{pvalue} generated from the test is 0.067. On the test, the significant value used is 0.05 so that based on algorithm, in that case it cannot immediately reject h0 and must continue compare the statistical value with the critical value, and the result states that the CDF latency in these cases has the same distribution with the baseline, so that regression is not detected. The same will apply to all significant values $<0.05$, but in the test with a significant value of 0.1,
the IS1 case will be detected as regression.

\begin{figure}[!htb]
	\centering
	\includegraphics[width=0.5\textwidth]{resources/ch4/log/1-log-new.png}
	\caption{\textit{Log} hasil pengujian kasus SI1 dengan alpha 0,05}
	\label{result_log_1}
\end{figure}

>>>>

\subsection{Overhead Testing}
Of the 11 test cases, the average PRA Engine tool uses 0.046
vCPU with standard deviation of 0.0038 and 154.41 MiB Memory with standard
deviation of 17.91 in one analysis. The entire cluster has resources
as much as 6 vCPUs and 22.5 GiB, so that in one time doing PRA Engine analysis
resulting in CPU overhead as much as 0.78\% and Memory as much as 0.67\% to the Kubernetes cluster. Overhead caused by the tool is low so that the use of PRA Engine tools will have no impact on the overall performance of the Kubernetes cluster. Table \ref{overhead-tbl} shows the result of the overhead testing.
\begin{table}[!htb]
	\caption{Overhead testing result}
	\label{overhead-tbl}
	\centering
	\begin{tabular}{|l|c|c|}
		\hline
		ID & CPU (vCPU) & Memory (MiB) \\
		\textbf{IS1}     & 0,042 & 137,82  \\ \hline
		\textbf{IS2}     & 0,043 & 128,71  \\ \hline
		\textbf{IS3}     & 0,04  & 131,55  \\ \hline
		\textbf{IS4}     & 0,045 & 146,6   \\ \hline
		\textbf{IS5}     & 0,046 & 153,61  \\ \hline
		\textbf{IS6}     & 0,047 & 152,71  \\ \hline
		\textbf{IS7}     & 0,048 & 152,71  \\ \hline
		\textbf{ES1}     & 0,049 & 168,8   \\ \hline
		\textbf{ES2}     & 0,05  & 183,68  \\ \hline
		\textbf{ES3}     & 0,051 & 176,59  \\ \hline
		\textbf{ES4}     & 0,052 & 165,75  \\ \hline
		\textbf{Average} & 0,046 & 154,411 \\ \hline
		\textbf{STD}     & 0,038 & 17,916  \\ \hline
	\end{tabular}
\end{table}
\pagebreak

@@

Fig. \ref{result_log_1} shows the log obtained from the IS1 case with a significant value 0.05. It can be seen that the \texttt{pvalue} generated from the test is 0.067. On the test, the significant value used is 0.05 so that based on algorithm, in that case it cannot immediately reject h0 and must continue compare the statistical value with the critical value, and the result states that the CDF latency in these cases has the same distribution with the baseline, so that regression is not detected. The same will apply to all significant values $<0.05$, but in the test with a significant value of 0.1,
the IS1 case will be detected as regression.
\begin{figure}[!htb]
	\centering
	\includegraphics[width=0.5\textwidth]{resources/ch4/log/1-log-new.png}
	\caption{\textit{Log} hasil pengujian kasus SI1 dengan alpha 0,05}
	\label{result_log_1}
\end{figure}

From the analyis above, therefore it can be interpreted that the use of significant values on the PRA Engine
will have an effect on the results, especially if the regression case to be detected does not
has a very significant change in its latency value as shown in
in the case of SI1. It can be concluded that the greater the significant value, the more
Also sensitive is the algorithm in detecting regressions that occur because they are not needed
very strong evidence to reject h0 but it means that h0 cannot be rejected by
too sure. Conversely, if the smaller the significant value used, the smaller the value will be
the stronger the evidence needed to reject h0 which means that h0 can be rejected
